manuscript

### 2025-01-29 doc/Manuscript.qmd
continue methods: robust design

## Title Title Title

@@

### Abstract

### Introduction

@@

### Methods

**Study area and species**

@@

**Capture-mark-recapture sampling**

*Sampling schedule*

@@

*Capturing & marking animals*

Field crews captured frogs by hand or dip net, and processed frogs at the point of capture. Crews first scanned each captured frog with a BioMark 601 passive integrated transponder (PIT) tag reader to detect if the frog was marked (i.e., a recapture). Crews then used calipers to measure the snout to urostyle (SUL) length of each captured frog, and released frogs \<40 mm SUL (which are considered subadults) without further processing. Crews continued collecting data on larger (\>40 mm SUL) frogs, which are considered adults. For new adult captures, crews inserted an 8 X 1.4 mm PIT tag under the dorsal skin using methods recommended by McAllister et al. (2004). Crews collected a GPS point (estimated precision error \~3 m) for each capture using a handheld Garmin GPS unit. Crews weighed each adult frog inside a tared plastic bag to the nearest 0.1 g using a Pesola spring scale. For each captured adult individual, crews only collected length and weight data during the first capture event within a three-day primary period. Afterward, if crews captured the same individual on a subsequent day duringthe same primary period, crews only recorded PIT tag, sex, and location data.

**Population modeling**

\
\
**Winter severity calculations**

### Results

### References

### Figures

>>>>

# Title Title Title

@@

## Abstract

## Introduction

@@

## Methods

### Study area and species

@@

### Capture-mark-recapture surveys

Capture-recapture sampling was conducted according to Pollock's [@pollock1982] robust design. Under the robust design, three primary survey periods occurred each summer from 2014 to 2018, each consisting of three consecutive survey days (secondary periods).

Field crews captured frogs by hand or dip net, and processed frogs at the point of capture. Crews first scanned each captured frog with a BioMark 601 passive integrated transponder (PIT) tag reader to detect if the frog was marked (i.e., a recapture). Crews then used calipers to measure the snout to urostyle (SUL) length of each captured frog, and released frogs \<40 mm SUL (which are considered subadults) without further processing. Crews continued collecting data on larger (\>40 mm SUL) frogs, which are considered adults. For new adult captures, crews inserted an 8 X 1.4 mm PIT tag under the dorsal skin using methods recommended by McAllister et al. (2004) [@mcallister2004]. Crews collected a GPS point (estimated precision error \~3 m) for each capture using a handheld Garmin GPS unit. Crews weighed each adult frog inside a tared plastic bag to the nearest 0.1 g using a Pesola spring scale. For each captured adult individual, crews only collected length and weight data during the first capture event within a three-day primary period. Afterward, if crews captured the same individual on a subsequent day during the same primary period, crews only recorded PIT tag, sex, and location data.

### Population modeling

@@

### Winter severity calculations

## Results

## References

## Figures
